cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-12-17 paper-cardinalR.Rmd
Updated Figure 6

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -0.6, 
                                              axis_pos_y = -0.6, 
                                              threshold = 0.022))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.55, 
                                              axis_pos_y = -0.55, 
                                              threshold = 0.016))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.2, 
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.04))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1, 
                                              axis_pos_x = -0.8, 
                                              axis_pos_y = -0.8, 
                                              threshold = 0.04))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.8,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.8, 
                                              axis_pos_y = -0.8, 
                                              threshold = 0.016))

>>>>

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.8,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.6, 
                                              axis_pos_y = -0.6, 
                                              threshold = 0.1))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 0.7,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.55, 
                                              axis_pos_y = -0.55, 
                                              threshold = 0.09))

@@

proj_obj1 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.2,
                                              axis_scaled = 1.7, 
                                              axis_pos_x = -1, 
                                              axis_pos_y = -1, 
                                              threshold = 0.1))

@@

proj_obj2 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1.2,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.8, 
                                              axis_pos_y = -0.8, 
                                              threshold = 0.1))

@@

proj_obj3 <- get_projection(projection = projection, 
                            centered_data = centered_data, 
                            axis_param = list(limits = 1,
                                              axis_scaled = 1.5, 
                                              axis_pos_x = -0.8, 
                                              axis_pos_y = -0.8, 
                                              threshold = 0.04))
